\begin{resumo}[Abstract]
This project consists of the construction of a Situational Awareness (SAW) assisted teaching supporting model. The SAW is widely used for the correct understanding of the environment and situations, being considered one of the main precursors of the Decision Making process, therefore, considering it's capabilities for understanding the universe in which it is used, SAW has the potential to be applied in Virtual Learning Environments (AVA). Also, the applicability of Educational Data Mining (EDM) techniques is also approached in this context, specifically in its application for developing methods for specific data types, these being generated from educational environments. Because of their inherent extreme dynamism, the AVAs require tools that can adapt themselves to the variations that emerge from the user's interaction with the environment. The EDM acts as an information processing motor, although the applicability is often restricted to the situation in which the technique was developed. The correct understanding of the situations surface during the interaction of the user with the AVA can create more efficient systems that would satisfy the educational learning process with greater efficacy. Viewing the environment in a conscious manner allows for the identification of each data configuration, and which possible action would be the best. This model must be capable of understanding the available contextual information, continually working to create and update the situations in which the EDM methods would be best applied and, from the feedback given by the execution of these methods, which, probabilistically speaking, best actions should be taken.

\noindent \textbf{Keywords:} Situation Awareness, Educational Data Mining, Virtual Learning Environment, Making Decision.
\end{resumo}